Analyzing TTC Delay Data to Improve Future Efficiency

### 2024-01-25 outputs/paper.qmd
Update figures

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-vstime1
#| fig-cap: "The amount of delays with respect to the time of day"
#| fig-width: 4

@@

bus_delay_data |>
  ggplot(aes(x = time)) +
  geom_histogram(fill = "blue", alpha = 0.75) +
  scale_x_time(breaks = scales::pretty_breaks(n = 12)) +
  xlab("Time") +
  ylab("Count") +
  theme_light() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  theme(axis.text=element_text(size=12),
      axis.title=element_text(size=14,face="bold"))

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-vstime2
#| fig-cap: "The amount of delays with respect to the time of day"
#| fig-width: 4

@@

subway_delay_data |>
  ggplot(aes(x=time)) +
  geom_histogram(fill = "red", alpha = 0.75) +
  scale_x_time(breaks = scales::pretty_breaks(n = 12)) +
  xlab("Time") +
  ylab("Count") +
  theme_light() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

@@

total_bus_delay_time_by_date |>
  ggplot(aes(x = date, y = total_delay_time)) + 
  geom_point() +
  geom_smooth(method = "loess") +
  theme_light()

total_bus_delay_time_by_date |>
  ggplot(aes(x = date, y = mean_delay_time)) + 
  geom_point() +
  geom_smooth(method = "loess") +
  theme_light()

>>>>

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-vstime1
#| fig-cap: "The amount of delays with respect to the time of day"
#| fig-width: 4
#| fig-height: 3

@@

bus_delay_data |>
  ggplot(aes(x = time)) +
  geom_histogram(fill = "blue", alpha = 0.75) +
  scale_x_time(breaks = scales::pretty_breaks(n = 12)) +
  xlab("Time") +
  ylab("Count") +
  theme_light() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-vstime2
#| fig-cap: "The amount of delays with respect to the time of day"
#| fig-width: 4
#| fig-height: 3

@@

subway_delay_data |>
  ggplot(aes(x=time)) +
  geom_histogram(fill = "red", alpha = 0.75) +
  scale_x_time(breaks = scales::pretty_breaks(n = 12)) +
  xlab("Time") +
  ylab("Count") +
  theme_light() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

@@

total_bus_delay_time_by_date |>
  ggplot(aes(x = date, y = total_delay_time)) + 
  geom_point() +
  geom_smooth(method = "loess") +
  theme_light() +
  xlab("Date") +
  ylab("Total Delay Time (Minutes)")

total_bus_delay_time_by_date |>
  ggplot(aes(x = date, y = mean_delay_time)) + 
  geom_point() +
  geom_smooth(method = "loess") +
  theme_light() +
  xlab("Date") +
  ylab("Total Delay Time (Minutes)")
